Trump vs. Harris: A Data-Driven Forecast modeling the 2024 US Presidential Elections

### 2024-10-22 paper/paper.qmd
Updated paper

---
title: "Trump vs. Harris: A Data-Driven Forecast modeling the 2024 US Presidential Elections"
author: 
  - Sophia Brothers
  - Deyi Kong
thanks: "Code and data are available at: [https://github.com/eeeee-cmd/US_Election/](https://github.com/eeeee-cmd/US_Election/)."
date: today
date-format: long
abstract: "This study models the 2024 U.S. Presidential election outcomes using advanced statistical techniques and predictive modeling. The analysis incorporates data from various polling sources and considers key demographic and political factors to forecast both the popular vote and Electoral College results. The findings suggest a close race between the two main candidates, Donald Trump and Kamala Harris, with a predicted victory for Trump in the Electoral College. This analysis contributes to understanding how public opinion data and electoral systems interact, providing insights into electoral dynamics in contemporary U.S. politics."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Trump vs. Harris: A Data-Driven Forecast modeling the 2024 US Presidential Elections"
author: 
  - Sophia Brothers
  - Deyi Kong
  - Rayan Awad Alim
thanks: "Code and data are available at: [https://github.com/eeeee-cmd/US_Election/](https://github.com/eeeee-cmd/US_Election/)."
date: today
date-format: long
abstract: "This study models the 2024 U.S. Presidential election outcomes using advanced statistical techniques and predictive modeling. The analysis incorporates data from various polling sources and considers key demographic and political factors to forecast both the popular vote and Electoral College results. The findings suggest a close race between the two main candidates, Donald Trump and Kamala Harris, with a predicted victory for Trump in the Electoral College. This analysis contributes to understanding how public opinion data and electoral systems interact, providing insights into electoral dynamics in contemporary U.S. politics."
format: pdf
number-sections: true
bibliography: references.bib
---
